Debiased Calibration for Generalized Two-Phase Sampling

### 2024-04-18 final/reports/prelim_paper.tex
Updated prelim paper. Hopefully done with topic 1.

%\textcolor{blue}{Also, the above equality is not true under two-phase sampling!)}
%\textcolor{red}{I agree that having the superscript $(1)$ and $(2)$ is
%  unnecessary. I have removed them. I have also modified the previous equation.
%  I agree that the invariance condition does not hold for two-phase sampling,
%  but if we consider $\pi_i$ as a function of $A_1$ then I believe this holds.
%  Is this correct? Should we not have $\pi_{i} = \pi_{1i} \pi_{2i|1}(A_1)$
%  because this is how conditional distributions work? (Also, I thought that this
%  is equivalent to the reverse sampling idea of Fey (1992), Shao and Steel
%(1999), and Kim et al. (2006).) I would love to discuss this with you.}

@@

%While this generalization is useful to an analyst who may want different
%properties of their estimator from maximum entropy estimation rather than the
%minimal squared loss, 
%% I am not sure if this is correct -----
%unless $\pi_{2i|1}^{-1} = x_i'a$ for some $a$, the
%estimator is not design consistent. 
%\footnote{ \textcolor{blue}{I do not understand this part.} 
%  \textcolor{red}{I changed the
%notation so that it would not be the unused column space notation. This is from
%Equation (11.17) of \cite{kim2024statistics}.}} 
%\footnote{\textcolor{red}{I think that I am confused about the purpose of having
%the assumption from Equation (11.17) in your sampling book. Could we discuss
%this?}}
%% --------------------------------------------

@@

%The proposed method will be something like this: 
%\textcolor{red}{Minimize 
%  $$ \sum_{i \in A_2} \frac{1}{\pi_i^{(1)}}  G( w_{2i} ) q_i $$ 
%  subject to 
%  $$ \sum_{i \in A_2} w_{2i}  x_i / \pi_i^{(1)} = \sum_{i \in A_1} x_i / \pi_i^{(1)}$$ 
%  and 
%  $$ \sum_{i \in A_2}  \frac{1}{\pi_i^{(1)}} w_{2i} g( \pi_{2i \mid 1}^{-1} ) q_i
%  = \sum_{i \in A_1}  \frac{1}{\pi_i^{(1)}}  g(\pi_{2i \mid 1}^{-1} ) q_i $$ 
%  where $g(\omega) = \partial G( \omega)/ \partial \omega$. }

% You need to show that the resulting calibration estimator $\hat{Y}_{\rm cal}=
% \sum_{i \in A_2} w_{1i} \hat{w}_{2i} y_i$ is asymptotically equivalent to the
% two-phase regression estimator in (\ref{reg}), where $w_{1i} = 1/ \pi_i^{(1)}$.

% Also, there should be a discussion about variance estimation. Once the
% linearization form is obtained, the formula for linearized variance estimation
% should be obtained easily.

@@

The first constraint is the existing calibration constraint and the second
ensures that design consistency is achieved. Here, 
$g(w) = \partial G / \partial w$. 
The original method of \cite{kwon2024debiased} only considered having finite
population quantities on the right hand side of \ref{eq:calconst1}.
Let $z_i = (x_i, g(\pi_{2i|1}^{-1}))$. Letting $w_{1i} = \pi_{1i}^{-1}$,
the the goal is to solve,

@@

%\begin{itemize}
%  \item[(A1)] $G(w)$ is strictly convex and twice differentiable in an interval
%    $\mathcal{V} \in \R$,
%  \item[(A2)] There exists $c_1, c_2 \in \mathcal{V}$ with $c_1, c_2 > 0$ such
%    that $c_1 < \pi_{2i|1} < c_2$ for $i = 1, \dots, n_2$, and 
%    that $c_1 < \pi_{1i} < c_2$ for $i = 1, \dots, n_1$,
%  \item[(A3)] If $\pi_{2ij|1}$ is joint inclusion probability of elements $i$
%    and $j$ in $A_2$, the Phase 2 sample and 
%    $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1}\pi_{2j|1}$ then,
%    $$\limsup_{n \to \infty} \max_{i,j \in U: i \neq j} |\Delta_{2ij|1}| <
%    \infty,$$
%    and if $\pi_{1ij}$ is the joint inclusion probability of elements $i$ and
%    $j$ in $A_1$, the Phase 1 sample and 
%    $\Delta_{1ij} = \pi_{1ij} - \pi_{1i}\pi_{1j}$ then,
%    $$\limsup_{n \to \infty} \max_{i,j \in U: i \neq j} |\Delta_{1ij}| <
%    \infty,$$
%  \item[(A4)] Assume that $\Sigma_z = \lim_{N \to \infty} \sum_{i \in U} z_i
%    z_i^T/N$ exists and is positive definite, the average fourth moment of $(y_i,
%    x_i^T)$ is finite ($\limsup_{N \to \infty} \sum_{i \in U} ||(y_i, x_i^T)||^4
%    / N < \infty$), and $\Gamma(\lambda) = \lim_{N \to \infty}  \sum_{i \in U}
%    f'(\lambda^T z_i) z_i z_i^T / N$ exists in a neighborhood around $\lambda_0
%    = (\bf 0, 1)$.
%\end{itemize}

%\begin{theorem}[Design Consistency]
%  Suppose that Conditions (A1) - (A4) hold. Then the solution $\hat w$ to 
%  Equation~\ref{eq:primalloss} subject to Equation~\ref{eq:calconst1} and 
%  Equation~\ref{eq:calconst2} 
%  exists and is unique with probability approaching 1. Furthermore, the
%  estimator $\hat \theta_{DCE} = \sum_{i \in A_2} \frac{\hat w_i y_i}{\pi_{1i}}$
%  satisfies
%
%  $$\hat \theta_{DCE} = \hat \theta_{DC} + o_p(n_2^{-1})$$
%
%  where $\hat \theta_{DC}$ is the debiased calibration estimator of 
%  \cite{kwon2024debiased}.
%
%\end{theorem}
%
%\begin{proof}
%  This proof follows the proof of \cite{kwon2024debiased} in a straightforward
%  manner. There are two main modifications that need to be made. The first is
%  that the proof needs to be written for two-phase sampling with $n_1$ and $n_2$
%  instead of a single $n$. The second is that we need to ensure that the result
%  still holds with an estimated population constraint that is $O_p(n_1^{-1/2})$
%  consistent.
%
%  With the Conditions (A1) - (A4) written with respect the the two-phase sample,
%  the first challenge is done. The second step largely holds from the existing
%  proof of \cite{kwon2024debiased} with modifications such as 
%
%  $$\hat Q(\lambda) = n_2^{-1} \sum_{i \in A_2} F(\lambda^T z_i^*) - n_1^{-1}
%  \lambda^T \sum_{i \in A_1} z_i^*$$ 
%
%  ensuring that our extension holds.
%
%%  \textcolor{red}{Dr. Kim, I know that I need to write up this proof in more
%%  detail, but I am unsure about the level of granularity that is required now. I
%%  can basically rewrite everything from the Appendix of \cite{kwon2024debiased}
%%  with the two-phase modification to show this result, but I don't know if I
%%  should yet.}
%\end{proof}

%We need the following additional assumptions to prove asymptotic normality.
%
%\begin{itemize}
%  \item[(B1)] 
%  \item[(B2)] The HT estimator is asymptotically normal under the sampling
%    design in the sense that 
%
%\end{itemize}

\begin{theorem}[Variance Estimation]
  Let $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1} \pi_{2j|1}$ and 
  $\hat \eta_i = z_i \hat \phi / q_i + \frac{\delta_{2i|1}}{\pi_{2i|1}} \left(y_i
  - z_i \hat \phi / q_i\right)$ where

  $$\hat \phi = \left[\sum_{i \in A_2} w_{1i}\left(\frac{z_i z_i^T}{
  g'(g^{-1}(g(d_{2i|1}) / q_i))q_i^2}\right)\right]^{-1} \sum_{i \in A_2} w_{1i}
    \left(\frac{z_i y_i}{g'(g^{-1}(g(d_{2i|1}) / q_i)) q_i}\right).$$

  An unbiased estimator of the variance of $\hat Y_{DCE}$ is

  \begin{align*}
    \hat V 
    &= \sum_{i \in A_1} \sum_{j \in A_1} \left(\frac{\pi_{1ij} -
    \pi_{1i}\pi_{1j}}{\pi_{1ij}}
    w_{1i} w_{1j} \hat \eta_i \hat \eta_j \right) \\ 
    &+ \sum_{i \in A_2} \sum_{j \in A_2} w_{1ij} w_{2ij|1} w_{2i|1} w_{2j|1} 
    \Delta_{2ij|1} (y_i - z_i \phi^* / q_i)(y_j - z_j \phi^* / q_j).
  \end{align*}
\end{theorem}

\begin{proof}
  First, we derive the solution for $\hat Y_{DCE}$, and then derive the
  asymptotic variance of this estimator using the linearization technique of
  \cite{randles1982asymptotic}.

  We want to solve Equation~\ref{eq:primalloss} subject to the constraints in
  Equations~\ref{eq:calconst1} and \ref{eq:calconst2}. Using the method of
  Lagrange multipliers we have a Lagrangian of

  $$\mathcal{L}(w_2) = -\sum_{i \in A_2} w_{1i} G(w_{2i})q_i + \lambda 
  \left(\sum_{i \in A_2} w_{1i} w_{2i} z_i - \sum_{i \in A_1} w_{1i} z_i\right).$$

  Our first order conditions yield,

  \begin{align*}
    0 &= \frac{\partial}{\partial w_{2i}} \mathcal{L}(w_{2}) \\ 
      &= -w_{1i} g(w_{2i}) q_i + \lambda w_{1i} z_i.
  \end{align*}

  This means that $\hat w_{2i} = g^{-1}(\hat \lambda z_i / q_i)$ and since $\hat
  \lambda$ is determined from the solution to Equations~\ref{eq:calconst1} and
  \ref{eq:calconst2}. Hence, $\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} 
  \hat w_{2i}(\hat \lambda) y_i$.

  To get the variance of $\hat Y_{DCE}$ we use the linearization technique of
  \cite{randles1982asymptotic}. First, notice that

  $$\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) y_i =
  \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) y_i + \left(
  \sum_{i \in A_1} w_{1i} z_i -
  \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) z_i\right)\phi
  := \hat Y_\ell(\hat \lambda, \phi).$$

  We can find the value of $\phi$ such that $E[\frac{\partial}{\partial
  \lambda}\hat Y_\ell(\lambda, \phi)]_{\lambda = \lambda^*}$ where $\lambda^*$
  is the probability limit of $\hat \lambda$. Notice, that 
  $\lambda^* = (\bf 0, 1)$ because $\hat w_{2i} \to \pi_{2i|1}^{-1}$. This means
  that the optimal value of $\phi$ solves,

  $$E\left[\frac{\partial}{\partial \lambda} \hat Y_\ell(\lambda, \phi)\right] =
  E\left[\sum_{i \in A_2} w_{1i} \frac{\partial}{\partial \lambda} w_{2i|1}(\lambda)
    y_i - \phi \sum_{i \in A_2} w_{1i} z_i \frac{\partial}{\partial \lambda}
    w_{2i|1}(\lambda) / q_i \right]$$

  which means that

  $$\phi^* = \left[\sum_{i \in U} \pi_{2i|1} \left(\frac{z_i z_i^T}{
    g'(g^{-1}(g(d_{2i|1}) / q_i))q_i^2}\right)\right]^{-1} \sum_{i \in U} \pi_{2i|1}
    \left(\frac{z_i y_i}{g'(g^{-1}(g(d_{2i|1}) / q_i)) q_i}\right).$$

  Hence,

  \begin{align*}
    \hat Y_\ell(\lambda^*, \phi^*) 
    &= \sum_{i \in A_2} w_{1i} \pi_{2i|1}^{-1}
    y_i + \left(\sum_{i \in A_1} w_{1i} z_i / q_i -
      \sum_{i \in A_2} w_{1i} \pi_{2i|1}^{-1} z_i / q_i\right)\phi^* \\ 
    &= \sum_{i \in A_1} w_{1i} \eta_i
  \end{align*}

@@

  $$\eta_i = z_i \phi^* / q_i + \frac{\delta_{2i|1}}{\pi_{2i|1}} \left(y_i
  - z_i \phi^* / q_i\right).$$

  To analyze the variance, consider the reverse framework of
  \cite{fay1992inferences}, \cite{kim2006replication}, and \cite{shao1999variance}.
  In this setup, we assume that $\mathcal{R} = \{\delta_{2i|1}\}_{i \in U}$ is
  known at the
  finite population level. Then with this we have,

  \begin{align*}
    V(\hat Y_{\ell}(\lambda^*, \phi^*)) 
    &= V\left(\sum_{i \in A_1} w_{1i} \eta_i(\phi^*)\right) \\
    &= V\left(E\left[\sum_{i \in A_1} w_{1i}\eta_i(\phi^*)\mid\mathcal{R}\right]\right) 
    +E\left[V\left(\sum_{i \in A_1} w_{1i} \eta_i(\phi^*)\mid\mathcal{R}\right)\right]\\
    &= V\left(\sum_{i \in U} \eta_i(\phi^*)\right) + E\left[\sum_{i \in U} 
    \sum_{j \in U} \Cov(\delta_{1i}, \delta_{1j}) 
    w_{1i} w_{1j} \eta_i(\phi^*) \eta_j(\phi^*)\right]\\
  \end{align*}

  We can estimate this variance using

  $$\hat V_{DCE} = \sum_{i \in A_1} \sum_{j \in A_1} \left(\frac{\pi_{1ij} -
  \pi_{1i}\pi_{1j}}{\pi_{1ij}}
    w_{1i} w_{1j} \hat \eta_i \hat \eta_j \right)
  $$

  for $\hat \eta_i = z_i \hat \phi / q_i + \frac{\delta_{2i|1}}{\pi_{2i|1}} \left(y_i
  - z_i \hat \phi / q_i\right)$ where

  $$\hat \phi = \left[\sum_{i \in A_2} w_{1i}\left(\frac{z_i z_i^T}{
  g'(g^{-1}(g(d_{2i|1}) / q_i))q_i^2}\right)\right]^{-1} \sum_{i \in A_2} w_{1i}
    \left(\frac{z_i y_i}{g'(g^{-1}(g(d_{2i|1}) / q_i)) q_i}\right).$$

  The problem with this estimator is that it is biased as $E[\hat V_{DCE}]$ is
  asymptotically equivalent to
  $V\left(\sum_{i \in A_1} w_{1i} \eta(\phi^*)\right)$. This yields a bias of

  \begin{align*}
    \text{Bias}(\hat V_{DCE}) 
    &= V\left(\sum_{i \in U} \eta_i(\phi^*)\right)\\ 
    &= \sum_{i \in U} \sum_{j \in U} \Delta_{2ij|1} w_{2i|1}
    w_{2j|1} (y_i - z_i \phi^* / q_i)(y_j - z_j \phi^* / q_j).
  \end{align*}

  where $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1} \pi_{2j|1}$. 
  However, we can estimate this bias with

  $$\widehat{\text{Bias}}(\hat V_{DCE}) = 
  \sum_{i \in A_2} \sum_{j \in A_2} w_{1ij} w_{2ij|1} w_{2i|1} w_{2j|1} 
  \Delta_{2ij|1} (y_i - z_i \phi^* / q_i)(y_j - z_j \phi^* / q_j).$$

@@

@@

%In contrast to the classical two-phase sampling framework, non-nested two-phase
%sampling involves two independent surveys conducted on the same target
%population. The key distinction is that the two samples, denoted as $A_1$ and
%$A_2$, are drawn independently rather than sequentially.  Table \ref{table:11-1}
%presents the data structure for non-nested two-phase sampling. 
%In the non-nested two-phase sampling, 
%a large probability sample $A_1$ is drawn from a finite population,  collecting
%only the $\bx$ variable, and  a  smaller sample $A_2$ is drawn from the same
%population, providing information  on both the $y$ and $\bx$ variables.
%It is assumed that the observed variable $x$ is comparable in the two surveys.
%\cite{renssen1997} formally addressed this non-nested two-phase sampling problem
%and 
%\cite{merkouris2004} extended the idea further to develop regression estimation
%combining information from multiple surveys. 
%\cite{kimrao12} considered the non-nested two-phase sampling in the context of
%mass imputation combining two independent surveys at the population and domain
%levels.
%\begin{table}[htb]
%\caption{Data Structure for non-nested two-phase sampling}
%\label{table:1}\par
%\vskip .2cm
%\centerline{\tabcolsep=3truept\begin{tabular}{|c|cc|}
%\hline
%Sample  & $X$ & $Y$ \\
%\hline
%$A_1$ & \checkmark &  \\
%$A_2$ & \checkmark & \checkmark  \\
%\hline
%\end{tabular}}
%\label{table:11-1}
%\end{table}
%To illustrate the non-nested two-phase sampling approach, let's consider the
%data structure shown in Table \ref{table:11-1}. This setup involves two
%independent samples, $A_1$ and $A_2$, drawn from the same target population.
%From these two samples, we can compute two unbiased estimators of the population
%total $\mathbf{X} = \sum_{i=1}^N \bx_i$ for the auxiliary variable x:
%$\hat{\mathbf{X}}_1 = \sum_{i \in A_1} \pi_{1i}^{-1} \bx_i$
%and 
%$\hat{\mathbf{X}}_2 = \sum_{i \in A_2} \pi_{2i}^{-1} \bx_i$. 
%Here, $\pi_{1i}$ and $\pi_{2i}$ represent the inclusion probabilities for
%samples $A_1$ and $A_2$, respectively.
%Both $\hat{\mathbf{X}}_1$ and $\hat{\mathbf{X}}_2$ are unbiased estimators of
%the population total $\mathbf{X}$ under the respective sampling designs. 
%The availability of these two unbiased estimators is a key feature of the
%non-nested two-phase sampling design, as it provides opportunities for
%developing enhanced estimation procedures combining information from different
%sources.  
%We can  construct a combined estimator of X, denoted as
%$\widehat{\mathbf{X}}_c$, as follows:
%\begin{equation}
%\widehat{\mathbf{X}}_c = W \hat{\mathbf{X}}_1 + (I - W) \hat{\mathbf{X}}_2, 
%\label{xgls}
%\end{equation}
%where $W$ is a $p \times p$ symmetric matrix of constants, and $p =
%\text{dim}(\bx)$ is the dimension of the auxiliary variable x. The optimal
%choice of the matrix W can be determined using the Generalized Least Squares
%(GLS) method. However, other choices of W can also be used. The key idea is to
%leverage the information from these two independent surveys to obtain a more
%accurate and efficient estimator of the population total X for the auxiliary
%variable x, compared to using only one of the surveys alone. 
%Using the combined estimator  $\widehat{\mathbf{X}}_{\rm c} $ in (\ref{xgls}),
%we can construct the following projection estimator:  
%\begin{equation}
% \widehat{Y}_p = \widehat{\mathbf{X}}_{\rm c}' \hat{\bm \beta}_q  
% \label{11-proj}
% \end{equation}
%where the regression coefficient estimator $\hat{\bm \beta}_q$ is defined as 
%$$ 
%\hat{\bm \beta}_q = \left( \sum_{i \in A_2} \bx_i \bx_i' / q_i \right)^{-1} 
%\sum_{i \in A_2} \bx_i y_i / q_i. 
%$$
%The choice of $q_i$ in the regression coefficient estimator is somewhat
%arbitrary. Two possible choices are:
%\begin{enumerate}
%\item Using the model variance under a regression superpopulation model.
%\item Using $q_i = \pi_{2i}^{-2} - \pi_{2i}^{-1}$ to compute the design-optimal regression estimator under Poisson sampling.
%\end{enumerate}
%The key idea is that by using the combined estimator $\widehat{\mathbf{X}}_c$ in
%the projection estimator $\widehat{Y}_p$, we can leverage the information from
%both the A1 and A2 samples to obtain a more accurate prediction of the variable
%of interest Y. The choice of $q_i$ allows for some flexibility in how the
%regression coefficient is estimated.
%To ensure the design-consistency of the projection estimator in (\ref{11-proj}),
%we can use the following regression estimator under non-nested two-phase
%sampling:
%\begin{equation}
%\widehat{Y}_{\rm tp, reg} = \widehat{Y}_2 + \left( \widehat{\mathbf{X}}_{\rm c} - \widehat{\mathbf{X}}_2 \right)' \hat{\bm \beta}_q
%\label{eq:11-28}
%\end{equation} 
%By the definition of $\widehat{\mathbf{X}}_{\rm c}$, we can also express this as: 
%\begin{equation}
%\widehat{Y}_{\rm tp, reg} = \widehat{Y}_2 + \left( \widehat{\mathbf{X}}_{1} - \widehat{\mathbf{X}}_2 \right)' \hat{\bm \alpha}_q,
%\label{eq:11-28}
%\end{equation} 
%where $\hat{\bm \alpha}_q = W \hat{\bm \beta}_q$.
%The key points are:
%\begin{enumerate}
%\item The design-consistent regression estimator $\widehat{Y}_{\rm tp, reg}$ is
%  constructed by adding a correction term to the projection estimator
%  $\widehat{Y}_p$ from the second sample.
%\item The regression estimator improves the efficiency of the  design unbiased
%  estimator  $\hat{Y}_2$ by substracting the projection of $\hat{Y}_2$ onto the
%  augmentation space \citep{tsiatis2006}, the linear space generated by 
% the difference between the combined estimator $\widehat{\mathbf{X}}_{\rm c}$
% and the estimator $\widehat{\mathbf{X}}_2$ from the second sample.
%\item 
%Alternatively, the augmentation space  can be expressed using the difference
%between the estimators $\widehat{\mathbf{X}}_{1}$ and $\widehat{\mathbf{X}}_2$,
%weighted by $\hat{\bm \alpha}_q$.
%\end{enumerate} 
%The goal is to leverage the information from both samples to obtain a
%design-consistent regression estimator for the variable of interest Y.
%Using the standard argument, we can obtain 
%\begin{eqnarray}
%\widehat{Y}_{\rm tp, reg} 
%&=& \widehat{Y}_2 +  \left( \widehat{\mathbf{X}}_{1} - \widehat{\mathbf{X}}_2 \right)' {\bm \alpha}_q^* + O_p(n^{-1} N) \label{eq:11-29}
%\end{eqnarray}
%where $\bm \alpha_q^*$ is the probability limit of $\hat{\bm \alpha}_q = W \hat{\bm \beta}_q$. By (\ref{eq:11-29}), 
% we can obtain 
%\begin{equation}
%V \left( \widehat{Y}_{\rm tp, reg}  \right) 
%= ({\bm \alpha}_q^* )' V \left( \widehat{\mathbf{X}}_{1}  \right) {\bm \alpha}_q^* + V\left( \hat{u}_2 \right) 
%\label{eq:11-31}
%\end{equation}
%where $\hat{u}_2 = \sum_{i \in A_2} \pi_{2i}^{-1} \left( y_i -  \bx_i'\bm
%\alpha_q^* \right) $. From the formula in (\ref{eq:11-31}), we can construct a
%linearized variance estimator. 
%Now, we can use the calibration weighting to construct the regression estimator
%under non-nested two-phase sampling. For  given the design weights $d_{2i} =
%\pi_{2i}^{-1}$, we find the minimizer of 

>>>>

@@

@@

@@

The first constraint is the existing calibration constraint and the second
ensures that design consistency is achieved. Here, 
$g(w) = \partial G / \partial w$. 
The original method of \cite{kwon2024debiased} only considered having finite
population quantities on the right hand side of \ref{eq:calconst1}.
Let $z_i = (x_i / q_i, g(\pi_{2i|1}^{-1}))$. Letting $w_{1i} = \pi_{1i}^{-1}$,
the the goal is to solve,

@@

\begin{theorem}[Design Consistency]
  Under regularity conditions,

  $$\hat Y_{DCE} = \hat Y_\ell(\lambda^*, \phi^*) + o_p(N / n_2)$$

@@

  $$\hat Y_{\ell}(\hat \lambda, \phi^*) = \hat Y_{DCE}(\hat \lambda) + 
  \left(\sum_{i \in A_1} w_{1i} z_i q_i = \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(\hat
  \lambda) z_i q_i\right)\phi^*$$

  $$\phi^* = 
  \left[\sum_{i \in U} \frac{\pi_{2i|1}z_i z_i^T q_i}{g'(d_{2i|1})}\right]^{-1}
  \sum_{i \in U} \frac{\pi_{2i|1}z_i y_i}{g'(d_{2i|1})}.$$

\end{theorem}

\begin{proof}
  In this proof, we derive the solution to Equation~\ref{eq:primal} and show
  that it is asymptotically equivalent to a regression estimator. Using the
  method of Lagrange multipliers, to solve Equation~\ref{eq:primal} we need to
  minimize,

  $$\mathcal{L}(w_{2|1}) = \sum_{i \in A_2} w_{1i} G(w_{2i|1}) q_i + 
  \lambda \left(\sum_{i \in A_2} w_{1i} w_{2i|1} z_i q_i - \sum_{i \in A_1} w_{1i}
  z_i q_i\right).$$

  The first order conditions show that

  $$\frac{\partial \mathcal{L}}{\partial w_{2i|1}}: g(w_{2i|1}) w_{1i}q_i +
    \lambda w_{1i} z_i q_i = 0.$$

  Hence, $\hat w_{2i}(\lambda) = g^{-1}(\lambda z_i)$ and $\hat \lambda$ is
  determined by the calibration condition. When the sample size gets large, we
  have $\hat w_{2i|1}(\hat \lambda) \to d_{2i|1}$ which means that $\hat \lambda
  \to \lambda^*$ where $\lambda^* = (\bf 0, 1)$. Then using the linearization
  technique of \cite{randles1982asymptotic}, we can construct a regression
  estimator,

  $$\hat Y_\ell(\hat \lambda, \phi)  = \hat Y_{DCE}(\hat \lambda) + 
  \left(\sum_{i \in A_1} w_{1i} z_i q_i - \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(\hat
  \lambda) z_i q_i\right)\phi.$$

  Notice that $\hat Y_\ell(\hat \lambda, \phi) = \hat Y_{DCE}(\hat \lambda)$ for
  all $\phi \in \mathbb{R}$. We choose $\phi^*$ such that

  $$E\left[\frac{\partial}{\partial \lambda} \hat Y_\ell(\lambda^*, \phi^*)\right]=0.$$

  Using the fact that $g^{-1}(\lambda^* z_i) = g^{-1}(g(d_{2i|1})) = d_{2i|1}$
  and $(g^{-1})'(x) = 1 / g'(g^{-1}(x))$, we have

  \begin{align*}
    \phi^*
    &= E\left[\sum_{i \in A_2} \frac{w_{1i}z_i z_i^T q_i}{g'(d_{2i|1})}\right]^{-1}
    E\left[\sum_{i \in A_2} \frac{w_{1i}z_i y_i}{g'(d_{2i|1})}\right]\\
    &= \left[\sum_{i \in U} \frac{\pi_{2i|1}z_i z_i^T q_i}{g'(d_{2i|1})}\right]^{-1}
    \left[\sum_{i \in U} \frac{\pi_{2i|1} z_i y_i}{g'(d_{2i|1})}\right]\\
  \end{align*}

  Thus, the linearization estimator is

  $$\hat Y_\ell(\lambda^*, \phi^*) = \sum_{i \in A_1} w_{1i} q_i z_i \phi^* +
  \sum_{i \in A_2} w_{1i} d_{2i|1} (y_i - q_i z_i \phi^*).$$

  By construction using a Taylor expansion yields,

  \begin{align*}
    \hat Y_{DCE}(\hat \lambda) 
    &= \hat Y_\ell(\lambda^*, \phi^*) + 
    E\left[\frac{\partial}{\partial \lambda}\hat Y_\ell(\lambda^*,
    \phi^*)\right](\hat \lambda - \lambda^*) + \frac{1}{2}
    E\left[\frac{\partial}{\partial \lambda^2} \hat Y_{DCE}(\lambda^*)\right] (\hat
    \lambda - \lambda^*)^2\\
    &= \hat Y_\ell(\lambda^*, \phi^*) + O(N)o_p(n_2^{-1}).
  \end{align*}

  The final equality comes from the fact that 
  $E\left[\frac{\partial}{\partial \lambda}\hat Y_\ell(\lambda^*, \phi^*)\right]
  = 0$, $\frac{\partial}{\partial \lambda^2} \hat w_{2i|1}(\lambda^*)$ is
  bounded and $|\hat \lambda - \lambda^*| = o_p(n_2^{-1/2})$, which proves our
  result.

@@

%\begin{proof}
%  First, we derive the solution for $\hat Y_{DCE}$, and then derive the
%  asymptotic variance of this estimator using the linearization technique of
%  \cite{randles1982asymptotic}.
%  We want to solve Equation~\ref{eq:primalloss} subject to the constraints in
%  Equations~\ref{eq:calconst1} and \ref{eq:calconst2}. Using the method of
%  Lagrange multipliers we have a Lagrangian of 
%  $$\mathcal{L}(w_2) = -\sum_{i \in A_2} w_{1i} G(w_{2i})q_i + \lambda 
%  \left(\sum_{i \in A_2} w_{1i} w_{2i} z_i - \sum_{i \in A_1} w_{1i} z_i\right).$$
%  Our first order conditions yield,
%  \begin{align*}
%    0 &= \frac{\partial}{\partial w_{2i}} \mathcal{L}(w_{2}) \\ 
%      &= -w_{1i} g(w_{2i}) q_i + \lambda w_{1i} z_i.
%  \end{align*}
%  This means that $\hat w_{2i} = g^{-1}(\hat \lambda z_i / q_i)$ and since $\hat
%  \lambda$ is determined from the solution to Equations~\ref{eq:calconst1} and
%  \ref{eq:calconst2}. Hence, $\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} 
%  \hat w_{2i}(\hat \lambda) y_i$.
%  To get the variance of $\hat Y_{DCE}$ we use the linearization technique of
%  \cite{randles1982asymptotic}. First, notice that 
%  $$\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) y_i =
%  \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) y_i + \left(
%  \sum_{i \in A_1} w_{1i} z_i -
%  \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) z_i\right)\phi
%  := \hat Y_\ell(\hat \lambda, \phi).$$
%  We can find the value of $\phi$ such that $E[\frac{\partial}{\partial
%  \lambda}\hat Y_\ell(\lambda, \phi)]_{\lambda = \lambda^*}$ where $\lambda^*$
%  is the probability limit of $\hat \lambda$. Notice, that 
%  $\lambda^* = (\bf 0, 1)$ because $\hat w_{2i} \to \pi_{2i|1}^{-1}$. This means
%  that the optimal value of $\phi$ solves,
%  $$E\left[\frac{\partial}{\partial \lambda} \hat Y_\ell(\lambda, \phi)\right] =
%  E\left[\sum_{i \in A_2} w_{1i} \frac{\partial}{\partial \lambda} w_{2i|1}(\lambda)
%    y_i - \phi \sum_{i \in A_2} w_{1i} z_i \frac{\partial}{\partial \lambda}
%    w_{2i|1}(\lambda) / q_i \right]$$
%  which means that
%  $$\phi^* = \left[\sum_{i \in U} \pi_{2i|1} \left(\frac{z_i z_i^T}{
%    g'(g^{-1}(g(d_{2i|1}) / q_i))q_i^2}\right)\right]^{-1} \sum_{i \in U} \pi_{2i|1}
%    \left(\frac{z_i y_i}{g'(g^{-1}(g(d_{2i|1}) / q_i)) q_i}\right).$$
%  Hence,
%  \begin{align*}
%    \hat Y_\ell(\lambda^*, \phi^*) 
%    &= \sum_{i \in A_2} w_{1i} \pi_{2i|1}^{-1}
%    y_i + \left(\sum_{i \in A_1} w_{1i} z_i / q_i -
%      \sum_{i \in A_2} w_{1i} \pi_{2i|1}^{-1} z_i / q_i\right)\phi^* \\ 
%    &= \sum_{i \in A_1} w_{1i} \eta_i
%  \end{align*}
%  where 
%  $$\eta_i = z_i \phi^* / q_i + \frac{\delta_{2i|1}}{\pi_{2i|1}} \left(y_i
%  - z_i \phi^* / q_i\right).$$
%  To analyze the variance, consider the reverse framework of
%  \cite{fay1992inferences}, \cite{kim2006replication}, and \cite{shao1999variance}.
%  In this setup, we assume that $\mathcal{R} = \{\delta_{2i|1}\}_{i \in U}$ is
%  known at the
%  finite population level. Then with this we have,
%  \begin{align*}
%    V(\hat Y_{\ell}(\lambda^*, \phi^*)) 
%    &= V\left(\sum_{i \in A_1} w_{1i} \eta_i(\phi^*)\right) \\
%    &= V\left(E\left[\sum_{i \in A_1} w_{1i}\eta_i(\phi^*)\mid\mathcal{R}\right]\right) 
%    +E\left[V\left(\sum_{i \in A_1} w_{1i} \eta_i(\phi^*)\mid\mathcal{R}\right)\right]\\
%    &= V\left(\sum_{i \in U} \eta_i(\phi^*)\right) + E\left[\sum_{i \in U} 
%    \sum_{j \in U} \Cov(\delta_{1i}, \delta_{1j}) 
%    w_{1i} w_{1j} \eta_i(\phi^*) \eta_j(\phi^*)\right]\\
%  \end{align*}
%  We can estimate this variance using 
%  $$\hat V_{DCE} = \sum_{i \in A_1} \sum_{j \in A_1} \left(\frac{\pi_{1ij} -
%  \pi_{1i}\pi_{1j}}{\pi_{1ij}}
%    w_{1i} w_{1j} \hat \eta_i \hat \eta_j \right)
%  $$
%  for $\hat \eta_i = z_i \hat \phi / q_i + \frac{\delta_{2i|1}}{\pi_{2i|1}} \left(y_i
%  - z_i \hat \phi / q_i\right)$ where 
%  $$\hat \phi = \left[\sum_{i \in A_2} w_{1i}\left(\frac{z_i z_i^T}{
%  g'(g^{-1}(g(d_{2i|1}) / q_i))q_i^2}\right)\right]^{-1} \sum_{i \in A_2} w_{1i}
%    \left(\frac{z_i y_i}{g'(g^{-1}(g(d_{2i|1}) / q_i)) q_i}\right).$$
%  The problem with this estimator is that it is biased as $E[\hat V_{DCE}]$ is
%  asymptotically equivalent to
%  $V\left(\sum_{i \in A_1} w_{1i} \eta(\phi^*)\right)$. This yields a bias of 
%  \begin{align*}
%    \text{Bias}(\hat V_{DCE}) 
%    &= V\left(\sum_{i \in U} \eta_i(\phi^*)\right)\\ 
%    &= \sum_{i \in U} \sum_{j \in U} \Delta_{2ij|1} w_{2i|1}
%    w_{2j|1} (y_i - z_i \phi^* / q_i)(y_j - z_j \phi^* / q_j).
%  \end{align*}
%  where $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1} \pi_{2j|1}$. 
%  However, we can estimate this bias with
%  $$\widehat{\text{Bias}}(\hat V_{DCE}) = 
%  \sum_{i \in A_2} \sum_{j \in A_2} w_{1ij} w_{2ij|1} w_{2i|1} w_{2j|1} 
%  \Delta_{2ij|1} (y_i - z_i \phi^* / q_i)(y_j - z_j \phi^* / q_j).$$
%\end{proof}

@@
